\CRANpkg{lg}: An R package for Local Gaussian Approximations

### 2021-08-17 otneim.tex
Third submission for the R Journal

Given a data set \code{x} having $n$ rows and $p \geq 2$ columns, the user must choose between four distinct estimation methods, and specify this choice by using the argument \code{est\_method} to the \code{lg\_main()}-function. We look at the built-in bivariate data set `faithful`, which records the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in the Yellowstone National Park, USA (see the help file in R for more details: \code{?faithful}), and load the \CRANpkg{lg}-package in order to demonstrate the implementation:

@@

Finally, the only thing that we must alter in order to perform the third test for serial cross-dependence is the bootstrap method. In the applications above, it suffices to use the standard bootstrap, where we resammple with replacement from the data. This is implemented in the \code{ind\_test()}-function by setting the \code{bootstrap\_type}-argument to \code{"plain"}, which is the default option. When testing for serial cross-dependence we need to use a block-bootstrap procedure, and \citet{laca:tjos:2018} consider two options here: The block bootstrap with either fixed \citep{kuns:1989} or random \citep{poli:roma:1994} block sizes, and this choice is specified by choosing \code{bootstrap\_type\ =\ "block"} or \code{bootstrap\_type\ =\ "stationary"}, respectively, in the call to \code{ind\_test()}. \citet{laca:tjos:2018} do not report significant differences in test performance using the different bootstrap types.

>>>>

Given a data set \code{x} having $n$ rows and $p \geq 2$ columns, the user must choose between four distinct estimation methods, and specify this choice by using the argument \code{est\_method} to the \code{lg\_main()}-function. We look at the built-in bivariate data set \code{faithful}, which records the waiting time between eruptions and the duration of the eruption for the Old Faithful geyser in the Yellowstone National Park, USA (see the help file in R for more details: \code{?faithful}), and load the \CRANpkg{lg}-package in order to demonstrate the implementation:

@@

Finally, the only thing that we must alter in order to perform the third test for serial cross-dependence is the bootstrap method. In the applications above, it suffices to use the standard bootstrap, where we resample with replacement from the data. This is implemented in the \code{ind\_test()}-function by setting the \code{bootstrap\_type}-argument to \code{"plain"}, which is the default option. When testing for serial cross-dependence we need to use a block-bootstrap procedure, and \citet{laca:tjos:2018} consider two options here: The block bootstrap with either fixed \citep{kuns:1989} or random \citep{poli:roma:1994} block sizes, and this choice is specified by choosing \code{bootstrap\_type\ =\ "block"} or \code{bootstrap\_type\ =\ "stationary"}, respectively, in the call to \code{ind\_test()}. \citet{laca:tjos:2018} do not report significant differences in test performance using the different bootstrap types.

### 2021-08-17 response3/response3.Rmd
Third submission for the R Journal

If we have used the same random seed this figure should be identical to what the reviewer has obtained. Whether the observed local correlations represent *significant* (in the statistical sense) dependence can be investigated by looking at the estimated standard deviations, and lower/upper confidence limits which is reporten on the 95% confidence level by default, available in the `dlg_object1` in the `$loc_cor_sd`, `$loc_cor_lower` and `$loc_cor_upper` slots respectively. By plotting the estimated correlations with their confidence intervals, as I have done below, we see that zero (represented as a horizontal line) is included in almost all of the intervals.

@@

**My response:** I confirm this behaviour on my side, and it turns out that this warning appeared after the 4.0 update of R (see `https://github.com/bstewart/stm/issues/222` for a discussion about this in relation to another package), and relates to the use of formulas in the `fGarch`-package. Fixing it requires an update to this package, so unfortunately I can not get rid of it in this example. It has not changed the results.

@@

**My response:** Yes, thank you for noticing. In order to make the examples as lightweight as possible I have demonstrated the methods on very small samples. The sample was a bit too small in this example, which caused problems in one of the dependencies; the `logspline`-package for estimating the marginal densities. I increased the length of the multivariate time series for this example slightly, which has eliminated the problem.

@@

>>>>

If we have used the same random seed this figure should be identical to what the reviewer has obtained. Whether the observed local correlations represent *significant*  dependence (in the statistical sense) can be investigated by looking at the estimated standard deviations, and lower/upper confidence limits which is reported on the 95% confidence level by default, available in the `dlg_object1` in the `$loc_cor_sd`, `$loc_cor_lower` and `$loc_cor_upper` slots respectively. By plotting the estimated correlations with their confidence intervals, as I have done below (the $x$-axis is just an index of the grid points), we see that zero (represented as a horizontal line) is included in almost all of the intervals.

@@

**My response:** I confirm this behavior on my side, and it turns out that this warning appeared after the 4.0 update of R (see `https://github.com/bstewart/stm/issues/222` for a discussion about this in relation to another package), and relates to the use of formulas in the `fGarch`-package. Fixing it requires an update to that package, so unfortunately I can not get rid of it in this example. It has not changed the results.

@@

**My response:** Yes, thank you for noticing. In order to make the examples as lightweight as possible I have demonstrated the methods on very small samples. The sample was a bit too small in this example, which caused problems in one of the dependencies; the `logspline`-package for estimating the marginal densities. I increased the length of the multivariate time series for this example, which has eliminated the problem.

@@

Finally, I have changed the order of lines 182 and 183 in the script in order to take care of a warning message regarding column names, resulting from a recent update in the `tibble`-package.
